---
title: "Forgiveness Prep Fund Vignette"
author: "Jon Spiegel"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
#This function takes in the amount of federal debt owed at the end of medical school, the interest rate at which it was borrowed, the income of the borrower, and how many years they plan to pay 10% of their income for
#It then calculates how much of the debt will be left each year after they have completed their term of repaying 10% of their income (on the final year, this debt will be forgiven and taxed)
#For example, suppose somebody borrowed $400,000 from the federal government and is becoming an oncologist (residency =5 years, average salary =$353,000)
#We will assume they borrowed at a rate of 7.5% and that they will pay it back over 20 years
    income <- c(65000,65000,65000,65000,65000, 353000, 353000,353000, 353000,353000, 353000,353000, 353000,353000, 353000,353000, 353000,353000, 353000,353000)
    income.driven.vector(400000,.075,income, plan=20)
#this gives us a final forgiven amount of $545732.1
    
    
    #income.driven is a highly similar function, the difference is that this returns the balance after each of the years in the form of a vector whereas income.driven returns only the final amount forgiven
    
```


