---
title: "Pay_Per_Year_Vignette"
author: "Jon Spiegel and Kevin Chen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Pay_Per_Year_Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The function `pay.per.year()` takes in your debt, its interest rate, your number of residency years, and the number of years after medical school at which point you would like to be done repaying all of your debt and returns the amount you need to pay per year to achieve this goal. It is assumed here that you will not be making payments during residency.

For example, say you owed 400,000 USD growing at a rate of 7.5% per year, have a 3-year residency, and want to finish paying 20 years after medical school. Then you would have:

```{r, fig.show='hold'}
library(MedLoans)
pay.per.year(400000, .075, 3, years = 20)
```
The last output value from `pay.per.year()` is the one that matters. Here, we see we would need to pay 48,632.41 USD per year for the first 17 years after residency in order to pay off our medical school debt.
    
The output from `pay.per.year()` can be tested using the functions `grow()` and `payments()`. First, grow the principle debt by however many years you will be in residency. Then put this grown value into `payments()`, with the appropirate interest rate and the payment output from `pay.per.year()`. The results should agree; for example, having it take you 20 minus the number of your residency years to finish your repayments at that rate. An example corresponding to this is shown below:

```{r, fig.show='hold'}
grow(400000, .075, 3)
payments(496918.8, .075, 48632)
```
