---
title: "Payments_Vignette"
author: "Jon Spiegel and Kevin Chen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Payments_Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The `payments()` function takes a fixed amount of money you will pay (`payment`) against your total debt (`base`) which is growing a fixed rate (`interest`) and will spit out a vector of 100 payments (or less if you have paid off your debt in less) with the amount owed at the end of each growth cycle (typcially a year).
    
For example, say you owed 100,000 USD growing at 7.5% per year and paid 10,000 USD per year against it:
```{r, fig.show='hold'}
MedLoans::payments(100000, .075, 10000)
```
`payments()` returns 3 outputs:
    
1. 17 is the number of years it will take to pay off the debt.
    
2. 165499 is the total number of dollars you will pay in paying off your debt.
    
3. The vector on the bottom displays how much is owed each of the 17 years of repayments.
    
This function pairs particularly well with first using the `pay.per.year()` function, which will tell you how much you need to pay per year to pay off your debt a chosen number of years after you finish medical school

