---
title: "Payments Vignette"
author: "Jon Spiegel"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
#payments takes a fixed amount of money you will pay (payment) against your total debt (base) which is growing a fixed rate (interest) and will spit out a vector of 100 payments (or less if you have paid off your debt in less) with the amount owed at the end of each growth cycle (typcially year)

#For example, say you owed $100,000 growing at 7.5% per year and paid $10,000 per year against it
payments(100000, .075, 10000)
    
#payments gives 3 outputs
  #17 is the number of years it will take to pay off the debt
  #165499 is the total number of dollars you will pay in paying off your debt
  #The vector on the bottom displays how much is owed each of the 17 years of repayments


#This function pairs particularly well with first using pay.per.year which will tell you how much you need to pay per year to pay off your debt a chosen number of years after you finish medical school
```


